NIDILRR requires applicants to include a Data Management Plan in the application. NIDILRR will review the data management plans of potential awardees for completeness and compliance before making the awards. The Data Management Plan does not count against the page limitation described in this FOA and is not subject to evaluation and scoring by the peer review panel.

\subsection{Data to be collected}
\begin{itemize}
    \item Description of the types and format of data to be collected, and how they will be organized, stored, and preserved.
    \item Description of metadata to be included in the data submission to a repository in order to enable meaningful and useful analysis of the data by users who are not part of the research team.
\end{itemize}

Indication of whether the awardee will submit the scientific data to ICPSR\footnote{applicants may seek technical assistance from the Interuniversity Consortium for Political and Social Research (ICPSR). ICPSR is the preferred data repository for archiving and sharing of scientific data generated under NIDILRR awards. ICPSR can be
accessed at \url{https://www.icpsr.umich.edu/icpsrweb/} or contact \email{help@icpsr.umich.edu} or 734- 647-2200.
} or another public data repository. If the data are to be submitted to ICPSR, no further justification is required. If another repository is identified, the awardee must provide a justification of how this repository will provide for a long-term preservation of, and public access to, scientific data in digital formats resulting from ACL/NIDILRR funded research at no cost. This justification should include a description of the way in which shared digital data will be discoverable, retrievable, and analyzable through the chosen data repository.

If applicable, explain why data sharing, long-term preservation, and access cannot be justified.

Provide a plan to address the study participants’ consent process to enable the de- identified data to be shared broadly for future research.

Indicate an estimated cost to implement the data management plan. This cost is allowable as part of the award’s direct costs.